Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-05-06 paper.tex
2^26 clarification
discarding bad child

The paper states that if these happen the child must be discarded. However it does not give instructions on how to proceed with the derivation. For example, an implementer could mark the index as forbidden and increment the child index.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|}
  \hline
  g & d  & D  \\
  \hline
  8 & 2 & 4 \\
  9 & 3 & 8 \\
  16 & 10 & 1024 \\
  32 & 20 & 1048576 \\
  \hline
  \end{tabular}
  \caption{Bits to randomize $g$ resulting in levels $D$.}
  \label{tab:g_and_d}
  \end{table}

@@

\section{Implementations}

>>>>

The paper states that if these happen the child must be discarded. However it does not give instructions on how to proceed with the derivation.

For example, an implementer could mark the index as forbidden and simply increment the child index. However, depending on the level, should the user share their extended public key to the world and others derive the same faulty child key, the security of the parent key would be degraded.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|}
  \hline
  g & d  & D  \\
  \hline
  8 & 2 & 4 \\
  9 & 3 & 8 \\
  16 & 10 & 1024 \\
  32 & 26 & 67108864 \\
  \hline
  \end{tabular}
  \caption{Bits to randomize $g$ resulting in levels $D$.}
  \label{tab:g_and_d}
  \end{table}

@@

It also becomes apparent that the recommended maximum level of depth in the BIP32-Ed25519 paper, $2^{20}$, is lower than the actual number of levels that can be performed without bit overflows, $2^{26}$. Indeed, $a_{j} \leq 2^{254} + 2^{253} + 2^{247} < 2^{254} + 2^{253} + 2^{252}$.
\section{Implementations}
